\chapter{Conclusion}%
\label{chapter:conclusion}

\begin{introduction}
The last chapter presents the conclusions of this dissertation.
\end{introduction} 


This dissertation focuses on the planning of the development of a vehicle maintenance web application for LightMobie's dealerships. 
The research on this topic reveals the importance of assuring quality of service in this market, presenting a paper to corroborate this statement.
The paper describes a study made in South Africa using the model SERVQUAL to measure the quality of service in the vehicle maintenance service.
This section also presents a web application using Laravel to increase the performance of the work at a dealership in Libya. 
The results were positive, however, the dealer's workers recommended some improvements to the system.

The development of the web application was based on the workflow of the research paper with an emphasis on quality service evaluation.
The application is also planned to integrate a recommendation from the \citet{MAS_MOTORS}, namely the introduction of an SMS service reminder. 


\section{Future work}

- internal messaging system to comunicate between the rececionist and the mechanics
- adicionar criar, remover, editar, ver category parts to the administrator
- allow mechanic to do tasks that aren't assigned to him
- remove passsword from user create and allow the employee to configure on email confirmation
- Assign multiple tasks to a mechanic
- Fazer estatisticas de média de tempo a resolver uma tarefa e de qualidade de serviço no workshop manager view
- quando um mecânico sair da plataforma durante uma tarefa fazer a pausa da tarefa antes de sair
- adicionar modulo de faturas que já existe na plataforma de bike sharing da lightmobie
- Add text to the client perception form to let them leave recommendation or final thougths
- allow the manager to change the parts needed for a task
- allow a mechanic to change the parts of a task before he starts it
- manager write a reason to deny the purchase